---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LigandReceptor

<!-- badges: start -->
<!-- badges: end -->

The goal of LigandReceptor is to simplify the process of identifying potential ligand-receptor pairs in scRNAseq data

## Installation

You can install LigandReceptor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chiblyaa/LigandReceptor")
```
## Example

To use this function, first obtain a list of genes expressed in a scRNAseq dataset using the SEURAT function FindAllMarkers():

```{r example}
## basic example code
library(Seurat)
library(LigandReceptor)

seuratDEGS <- LigandReceptor::test_dataset #test_dataset obtained using FindAllMarkers from SEURAT
ncells = 23 #number of unique cell identities in SEURAT object
celltypelabels = as.vector(unique(test_dataset$cluster)) # create vector of cell identities
colors = topo.colors(ncells) # create vector of colors of length = ncells
LRdatabase <- LigandReceptor::LRdatabase # Load ligand-receptor pair reference database

## This will generate a table with ligand-receptor pair for the specified cell types in celltypelabels
LR.pairs <- LigandReceptorPairsTable(ncells, celltypelabels, seuratDEGS, LRdatabase)

# This will generate the chord plot associated with the table
#PairsPlot <- function(filename, ncells, celltypelabels, cellcolors, seuratDEGS, LRdatabase, subsetgenes, from = celltypelabels, to = celltypelabels)

```

The generated table looks like this:

```{r table}
head(LR.pairs, 10)
```

The corresponding plot would look like this:

```{r plot, echo = FALSE}
### TBD
```


