---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LigandReceptor

<!-- badges: start -->
<!-- badges: end -->

The goal of LigandReceptor is to simplify the process of identifying potential ligand-receptor pairs in scRNAseq data

## Installation

You can install LigandReceptor from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chiblyaa/LigandReceptor")
```
## Example

To use this function, first obtain a list of genes expressed in a scRNAseq dataset using the SEURAT function FindAllMarkers().
An example of an acceptable table:
```{r testdata, echo=FALSE, results='asis'}
test_dataset <- LigandReceptor::test_dataset
test_dataset <- test_dataset[test_dataset$cluster %in% c("Acinar", "Myoepithelial", "End bud", "Stromal", "Krt19+ duct",
                                                         "Basal duct", "Macrophages"),]
knitr::kable(test_dataset[1:5,], caption = "A test scRNAseq dataset:")
LRdatabase <- LigandReceptor::LRdatabase # Load ligand-receptor pair reference database
```

Basic example code for generating a table with ligand-receptor pairs:
```{r example}

library(LigandReceptor)
## This will generate a table with ligand-receptor pair for the specified cell types in celltypelabels
LR.pairs <- LigandReceptorPairsTable(seuratDEGS = test_dataset, LRdatabase = LRdatabase)
knitr::kable(LR.pairs[1:10,], caption = "Ligand-Receptor pairs: ")
```

Chord plot to represent ligands from Myoepithelial cells to all other cells:
```{r plot}
# This will generate the chord plot associated with the table
colors = topo.colors(as.numeric(length(unique(test_dataset$cluster)))) # create vector of colors of length = ncells
names(colors) <- as.character(unique(test_dataset$cluster))

PairsPlot(cellcolors=colors, seuratDEGS = test_dataset, LRdatabase)
legend("bottomright",   # location of legend
      legend = names(colors), # categories or elements to render in
			 # the legend
      fill = colors) 
```





